```{r, message = FALSE, warnings = FALSE}
#devtools::install_github("https://github.com/MandyKarnauskas-NOAA/plotTimeSeries.git")

library(plotTimeSeries)
library(spam)
```

# 5. Tracking performance toward fishery management objectives

## 5.1 Food production

### Fishery independent surveys of economically important species

Indicator 16

### Commercial landings

Indicator 17

### Maximum length and size structure

Indicator 18

### Changes in target species / landing composition

Indicator 20

## 5.2 Socioeconomic health

### Total, lobster and conch revenues

Indicator 21

### Total, lobster and conch trips

Indicator 22

### Ocean economy employment and wages

Indicator 23

```{r}
load("../indicator_objects/OceanNAICS.RData")
plotIndicatorTimeSeries(inddata, coltoplot = 1:2, plotrownum = 2, trendAnalysis = F, sublabel = T)
```

### GDP

Indicator 24

### Unemployment

Indicator 25

## 5.3 Equity

### Gini coefficient for distribution of landings and revenue

Indicator 26

```{r}
load("../indicator_objects/gini.RData")
plotIndicatorTimeSeries(inddata, coltoplot = 1:2, plotrownum = 2, trendAnalysis = F, sublabel = T)
```

### Commercial fishing community engegement and reliance

Indicator 27

## 5.4 Engagement and participation

### Recreational fishing engagement and participation

Indicator 28

### Commercial fishing engagement and participation

Indicator 29

## 5.5 Bycatch reduction

### Changes in gear type

Indicator 30

## 5.5 Governance

### Number of seasonal closures implemented

Indicator 31

### Number of education and outreach events

Indicator 32

### Number of enforcement actions

Indicator 33

## 5.6 Protection of ecosystems

### Percent coral cover and coral species richness

Indicator 34

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/NCRMP_coral_cover_richness.RData")
plotIndicatorTimeSeries(inddata, trendAnalysis = F)
```

### Coral species diversity

Indicator 35
