```{r, message = FALSE, warnings = FALSE}
#devtools::install_github("https://github.com/MandyKarnauskas-NOAA/plotTimeSeries.git")

library(plotTimeSeries)
library(spam)
```

# 4. Risks to meeting fishery management objectives

### Degree heating weeks

Indicator 1

DegreeHeatingWeeks.RData doesn't work. Think it's an issue with the date column. Also called ind not inddata.

### Ocean acidification via aragonite saturation state

Indicator 2

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/OA.RData")
plotIndicatorTimeSeries(inddata, trendAnalysis = T)
```

### Hurricane activity

Indicator 3

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/ACEindex.RData")
plotIndicatorTimeSeries(ind, trendAnalysis = T)
```

### Turbidity

Indicator 4

turbidity.RData doesn't work. Again looks like an issue with the date.

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/turbidity.RData")
plotIndicatorTimeSeries(ind, coltoplot = 1:3, plotrownum = 2, trendAnalysis = T)
```

### Sea surface temperature

Indicator 5

No RData file for SST


### Marine debris

Indicator 6

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/beach_litter_un_carib.RData")
plotIndicatorTimeSeries(inddata, trendAnalysis = F)
```

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/marine_debris.RData")
plotIndicatorTimeSeries(inddata, trendAnalysis = F)
```

### Identified point source pollution sites

Indicator 7

### Primary productivity via ocean color

Indicator 8

carib_Chl.RData doesn't work. Another issue with the date.

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/carib_Chl.RData")
plotIndicatorTimeSeries(ind, trendAnalysis = F)
```

### Coastal development via land cover

Indicator 9

### Number of major earthquakes

Indicator 10

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/earthquakes.RData")
plotIndicatorTimeSeries(ind, trendAnalysis = T)
```

### Fishery/market disturbance indicator (maybe belongs in socioeconomic health)

Indicator 11

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/disturbance.RData")
plotIndicatorTimeSeries(inddata, coltoplot = 1:3, trendAnalysis = T, sublabel = T)
```

### Sargassum inundation

Indicator 12

doesn't work

load("indicator_objects/Sargassum.RData") 
plotIndicatorTimeSeries(inddata, coltoplot = 1:2, plotrownum = 2, trendAnalysis = F, sublabel = T) 

load("indicator_objects/sargassum_innundation_monthly_mean_hu.RData")
plotIndicatorTimeSeries(inddata, coltoplot = 1:2, plotrownum = 2, trendAnalysis = F, sublabel = T)

### Tourism via hotel occupancy

Indicator 13

doesn't work 

load("indicator_objects/hotel_occupancy_rates_USVI_and_PR.RData")
plotIndicatorTimeSeries(inddata, trendAnalysis = F) 

load("indicator_objects/hotel_occupancy.RData") 
plotIndicatorTimeSeries(inddata, trendAnalysis = F) 

### Population density

Indicator 14

### Population change

Indicator 15