```{r, message = FALSE, warnings = FALSE}
#devtools::install_github("https://github.com/MandyKarnauskas-NOAA/plotTimeSeries.git")

library(plotTimeSeries)
library(spam)
```

# 4. Risks to meeting fishery management objectives

### Degree heating weeks

Indicator 1

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/DegreeHeatingWeeks.RData")
plotIndicatorTimeSeries(ind, coltoplot = 1:2, trendAnalysis = T, sublabel = T, dateformat = "%Y%m", plotrownum = 2, plotcolnum = 1)
```

### Ocean acidification via aragonite saturation state

Indicator 2

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/OA.RData")
plotIndicatorTimeSeries(inddata, trendAnalysis = T)
```

### Hurricane activity

Indicator 3

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/ACEindex.RData")
plotIndicatorTimeSeries(ind, trendAnalysis = T)
```

### Turbidity

Indicator 4

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/turbidity.RData")
plotIndicatorTimeSeries(ind, coltoplot = 1:3, plotrownum = 2, trendAnalysis = T, dateformat = "%m-%Y", sublabel = T)
```

### Sea surface temperature

Indicator 5

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/Carib_SST.RData")
plotIndicatorTimeSeries(ind, coltoplot = 1:3, trendAnalysis = T, sublabel = T, dateformat = "%m-%Y")
```


### Marine debris

Indicator 6

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/beach_litter_un_carib.RData")
plotIndicatorTimeSeries(inddata, trendAnalysis = F)
```

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/marine_debris.RData")
plotIndicatorTimeSeries(inddata, trendAnalysis = F)
```

### Identified point source pollution sites

Indicator 7

### Primary productivity via ocean color

Indicator 8

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/carib_Chl.RData")
plotIndicatorTimeSeries(ind, trendAnalysis = T, dateformat = "%m-%Y")
```

### Coastal development via land cover

Indicator 9

### Number of major earthquakes

Indicator 10

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/earthquakes.RData")
plotIndicatorTimeSeries(ind, trendAnalysis = T)
```

### Fishery/market disturbance indicator (maybe belongs in socioeconomic health)

Indicator 11

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/disturbance.RData")
plotIndicatorTimeSeries(inddata, coltoplot = 1:3, trendAnalysis = T, sublabel = T)
```

### Sargassum inundation

Indicator 12

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/Sargassum.RData")
plotIndicatorTimeSeries(inddata, trendAnalysis = T)
```

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/sargassum_innundation_monthly_mean_hu.RData")
plotIndicatorTimeSeries(inddata, coltoplot = 1:3, sublabel = T, trendAnalysis = T, dateformat = "%Y%b")
```

### Tourism via hotel occupancy

Indicator 13

```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/hotel_occupancy_rates_USVI_and_PR.RData")
plotIndicatorTimeSeries(inddata, coltoplot = 1:2, sublabel = T, trendAnalysis = T, dateformat = "%Y%b")
```
```{r, message = FALSE, warnings = FALSE}
load("../indicator_objects/hotel_occupancy.RData")
plotIndicatorTimeSeries(inddata, coltoplot = 1:2, sublabel = T, trendAnalysis = T, dateformat = "%Y%b")
```


### Population density

Indicator 14

### Population change

Indicator 15